Repeatability Test

### 2017-05-24 pt_characterization/rep_check/1024_run.tex
New draft for concrete complexity

@@

\begin{figure}[hp!]
	\centering
	\subfigure[ET frequency on INC1024-Run1]{
		\includegraphics[scale=0.43]{1024_run/1024_sec_et_hist1.eps}
		\label{fig:inc1024_run1_et}
	}
	\subfigure[ET frequency on INC1024-Run2]{
		\includegraphics[scale=0.43]{1024_run/1024_sec_et_hist2.eps}
		\label{fig:inc1024_run2_et}
	}
	\subfigure[ET frequency on INC1024-Run3]{
		\includegraphics[scale=0.43]{1024_run/1024_sec_et_hist3.eps}
		\label{fig:inc1024_run3_et}
	}
	\caption{ET Histograms of Three Consecutive INC4096 Runs\label{fig:s9_inc1024_et}}
\end{figure}

@@

\begin{figure}[hp!]
	\centering
	\subfigure[PT frequency on INC1024-Run1]{
		\includegraphics[scale=0.43]{1024_run/1024_sec_pt_hist1.eps}
		\label{fig:inc1024_run1_pt}
	}
	\subfigure[PT frequency on INC1024-Run2]{
		\includegraphics[scale=0.43]{1024_run/1024_sec_pt_hist2.eps}
		\label{fig:inc1024_run2_pt}
	}
	\subfigure[PT frequency on INC1024-Run3]{
		\includegraphics[scale=0.43]{1024_run/1024_sec_pt_hist3.eps}
		\label{fig:inc1024_run3_pt}
	}
	\caption{PT Histograms of Three Consecutive INC4096 Runs\label{fig:s9_inc1024_pt}}
\end{figure}

>>>>

\clearpage

@@

\begin{figure}[hp!]
	\centering
	\subfigure[ET frequency on INC1024-Run1]{
		\includegraphics[scale=0.43]{1024_run/1024_sec_et_hist1.eps}
		\label{fig:inc1024_run1_et}
	}
	\subfigure[ET frequency on INC1024-Run2]{
		\includegraphics[scale=0.43]{1024_run/1024_sec_et_hist2.eps}
		\label{fig:inc1024_run2_et}
	}
	\subfigure[ET frequency on INC1024-Run3]{
		\includegraphics[scale=0.43]{1024_run/1024_sec_et_hist3.eps}
		\label{fig:inc1024_run3_et}
	}
	\caption{ET Histograms of Three Consecutive INC1024 Runs\label{fig:s9_inc1024_et}}
\end{figure}

@@

\begin{figure}[hp!]
	\centering
	\subfigure[PT frequency on INC1024-Run1]{
		\includegraphics[scale=0.43]{1024_run/1024_sec_pt_hist1.eps}
		\label{fig:inc1024_run1_pt}
	}
	\subfigure[PT frequency on INC1024-Run2]{
		\includegraphics[scale=0.43]{1024_run/1024_sec_pt_hist2.eps}
		\label{fig:inc1024_run2_pt}
	}
	\subfigure[PT frequency on INC1024-Run3]{
		\includegraphics[scale=0.43]{1024_run/1024_sec_pt_hist3.eps}
		\label{fig:inc1024_run3_pt}
	}
	\caption{PT Histograms of Three Consecutive INC1024 Runs\label{fig:s9_inc1024_pt}}
\end{figure}

### 2017-05-24 pt_characterization/rep_check/paper.tex
new draft for repeatability
April 27 draft
New draft for concrete complexity

\documentclass[10pt]{article}
\usepackage[margin=1in]{geometry}
 \usepackage{auto-pst-pdf}
\usepackage{graphicx}
%\usepackage{arydshln}
\usepackage{ifpdf}
\ifpdf
  \usepackage{epstopdf}
\fi
\usepackage{multirow}
\usepackage{epsfig}
\usepackage{float}
\usepackage{url}
\usepackage{color}
\usepackage{subfigure}

@@

\section{Description}
This document presents two sets of histograms based on the two runs 
of a program under test, called {\em INC}, with a set of increasing task lengths 
from 1 second to 4096 seconds.
We would like to see if both of the sets have the same shape for the same task length.
If so then, we can say that run repeatability is satisfied in our experiment setting. 
In this study the used protocol is equivalent to SEDONA, eliminating samples involving infrequent, long-running daemons, which is the first step of EMPv5. In other words, the protocol skips the second step 
of EMPv5 that removes samples with process times over/below two standard deviations 
from the average after performing the first step.

@@

>>>>

\documentclass[10pt]{article}
\usepackage[margin=1in]{geometry}
 \usepackage{auto-pst-pdf}
\usepackage{graphicx}
\usepackage{footnote}
%\usepackage{arydshln}
\usepackage{ifpdf}
\ifpdf
  \usepackage{epstopdf}
\fi
\usepackage{multirow}
\usepackage{epsfig}
\usepackage{float}
\usepackage{url}
\usepackage{color}
\usepackage{subfigure}

@@

\section{Description}
This document presents two sets of histograms based on the two runs 
of a program under test, called {\em INC}, with a set of increasing task lengths 
from 1 second to 4096 seconds.
We would like to see if both of the sets have the same shape for the same task length.
If so then, we can say that run repeatability is satisfied in our experiment setting. 
In this study the used protocol is equivalent to SEDONA~\cite{Sedona}, 
eliminating samples involving infrequent, long-running daemons, which is the first step of EMPv5.

In the SEDONA protocol, we use taskstats C struct to get measures of a captured process. 
The taskstat's data is delivered via a netlink socket from the kernel space. 
The receive buffer for the socket is not robust for many observed processes~\cite{Metrology}. 
Fortunately, there is an average of 95 processes per iteration of a run, 
which turns out to be fine with the struct. 
For a much more number of processes, 
the use of  {\tt /proc/}[pid]{\tt{/stat}} is preferred, 
as (i) there are equivalent measures available in the {\tt /proc} filesystem, 
and (ii) there's little constraint on the use as opposed to taskstats.

@@

\input{10k_run.tex}

\input{u_s_time.tex}

\input{1024_run.tex}

\bibliographystyle{abbrv}
\newcommand{\etalchar}[1]{$^{#1}$}
\begin{thebibliography}{99}
\vspace{0.1em}
\bibitem
%{Avnur:2000:ECA:342009.335420}
{Sedona}
Young-Kyoon Suh, ``SEDONA: A Novel Protocol for Identifying Infrequent, Long-running Daemons on a Linux System'', in {\em IEICE Transactions on Information Systems}, Vol. 100D, No. 9, pp.~??--??, 2017.
\vspace{0.1em}
\bibitem
%{Avnur:2000:ECA:342009.335420}
{Metrology}
Sabah Currim,Richard T. Snodgrass, Young-Kyoon Suh, and Rui Zhang, ``DBMS Metrology: Measuring Query Time'', in {\em ACM Transactions on Database Systems}, 42(1):3:1--42(+8), 2017.
\end{thebibliography}

### 2017-05-24 pt_characterization/rep_check/res2.tex
New draft for concrete complexity

\begin{table}[h]
\begin{center}
\begin{tabular}{|p{2cm}|p{3cm}|p{3cm}|p{4cm}|p{3.5cm}|} \hline
Machine & Task Length (sec) & Description & Experiment Period & Relevant \linebreak Histograms\\ \hline
{\tt sodb9} &  INC1$\sim$INC64 & 1000 samples, each & 2017-03-13 $\sim$ 2017-03-14 & Figs.~\ref{fig:s9_r2_et_hist1},~\ref{fig:s9_r2_et_hist2},~\ref{fig:s9_r2_pt_hist1}, and~\ref{fig:s9_r2_pt_hist2}\\ \hline
{\tt sodb9} &  INC128$\sim$INC1024 & 300 samples, each & 2017-03-14 $\sim$ 2017-03-21 & 
Figs.~\ref{fig:s9_r2_et_hist3} and~\ref{fig:s9_r2_pt_hist3}\\ \hline
{\tt sodb10} & INC2048 & 300 samples & 2017-03-13 $\sim$ 2017-03-20 & Figs.~\ref{fig:inc2048_r2_et_hist_v5} and~\ref{fig:inc2048_r2_hist_v5}\\ \hline
{\tt sodb12} & INC4096 & 300 samples & 2017-03-02 $\sim$ 2017-03-17 & Figs.~\ref{fig:inc4096_r2_et_hist_v5} and~\ref{fig:inc4096_r2_hist_v5}\\ \hline
\end{tabular}
\end{center}
\vspace{-.2in}
\caption{Notes on experiment runs used for histograms\label{tab:exp_notes2}}
\end{table}

@@

\begin{figure}[hp!]
	\centering
	\subfigure[ET frequency on INC2048]{
		\includegraphics[scale=0.43]{repet_data2/2048_sec_et_hist_v5.eps}
		\label{fig:inc2048_r2_et_hist_v5}
	}
	\subfigure[ET frequency on INC4096]{
		\includegraphics[scale=0.43]{repet_data2/4096_sec_et_hist_v5.eps}
		\label{fig:inc4096_r2_et_hist_v5}
	}
	\caption{ET Histograms of INC2048 and INC4096~\label{fig:s9_r2_et_hist4}}
\end{figure}

@@

\begin{figure}[t]
	\centering
	\subfigure[PT frequency on INC2048]{
		\includegraphics[scale=0.43]{repet_data2/2048_sec_pt_hist_v5.eps}
		\label{fig:inc2048_r2_hist_v5}
	}
	\subfigure[PT frequency on INC4096]{
		\includegraphics[scale=0.43]{repet_data2/4096_sec_pt_hist_v5.eps}
		\label{fig:inc4096_r2_hist_v5}
	}
	\caption{PT Histograms of INC2048 and INC4096~\label{fig:s9_r2_pt_hist4}}
\end{figure}

>>>>

\begin{table}[h]
\begin{center}
\begin{tabular}{|p{2cm}|p{3cm}|p{3cm}|p{4cm}|p{3.5cm}|} \hline
Machine & Task Length (sec) & Description & Experiment Period & Relevant \linebreak Histograms\\ \hline
{\tt sodb9} &  INC1$\sim$INC64 & 1000 samples, each & 2017-03-13 $\sim$ 2017-03-14 & Figs.~\ref{fig:s9_r2_et_hist1},~\ref{fig:s9_r2_et_hist2},~\ref{fig:s9_r2_pt_hist1}, and~\ref{fig:s9_r2_pt_hist2}\\ \hline
{\tt sodb9} &  INC128$\sim$INC1024 & 300 samples, each & 2017-03-14 $\sim$ 2017-03-21 & 
Figs.~\ref{fig:s9_r2_et_hist3} and~\ref{fig:s9_r2_pt_hist3}\\ \hline
{\tt sodb10} & INC2048 & 300 samples & 2017-03-13 $\sim$ 2017-03-20 & Figs.~\ref{fig:inc2048_r2_et_hist_v5} and~\ref{fig:inc2048_r2_hist_v5}\\ \hline
{\tt sodb12} & INC4096 & 300 samples & 2017-03-02 $\sim$ 2017-03-17 & Figs.~\ref{fig:inc4096_r2_et_hist_v5} and~\ref{fig:inc4096_r2_hist_v5}\\ \hline
{\tt sodb10} & INC8192& 261 samples & 2017-04-27 $\sim$ 2017-05-21 & Figs.~\ref{fig:inc8192_r2_et_hist_v5} and~\ref{fig:inc8192_r2_hist_v5}\\ \hline
{\tt sodb12} & INC16384& 130 samples & 2017-04-27 $\sim$ 2017-05-21 & Figs.~\ref{fig:inc16384_r2_et_hist_v5} and~\ref{fig:inc16384_r2_hist_v5}\\ \hline
\end{tabular}
\end{center}
\vspace{-.2in}
\caption{Notes on experiment runs used for histograms\label{tab:exp_notes2}}
\end{table}

INC8192/INC16384 unfortunately stopped in the middle of their runs due to a frozen vnc problem. So couldn't finish 300 samples.

@@

\begin{figure}[hp!]
	\centering
	\subfigure[ET frequency on INC2048]{
		\includegraphics[scale=0.43]{repet_data2/2048_sec_et_hist_v5.eps}
		\label{fig:inc2048_r2_et_hist_v5}
	}
	\subfigure[ET frequency on INC4096]{
		\includegraphics[scale=0.43]{repet_data2/4096_sec_et_hist_v5.eps}
		\label{fig:inc4096_r2_et_hist_v5}
	}
	\subfigure[ET frequency on INC8192]{
		\includegraphics[scale=0.43]{repet_data2/8192_sec_et_hist.eps}
		\label{fig:inc8192_r2_et_hist_v5}
	}
	\subfigure[ET frequency on INC16384]{
		\includegraphics[scale=0.43]{repet_data2/16384_sec_et_hist.eps}
		\label{fig:inc16384_r2_et_hist_v5}
	}
	\caption{ET Histograms of INC2048 ... INC16384~\label{fig:s9_r2_et_hist4}}
\end{figure}

@@

\begin{figure}[t]
	\centering
	\subfigure[PT frequency on INC2048]{
		\includegraphics[scale=0.43]{repet_data2/2048_sec_pt_hist_v5.eps}
		\label{fig:inc2048_r2_hist_v5}
	}
	\subfigure[PT frequency on INC4096]{
		\includegraphics[scale=0.43]{repet_data2/4096_sec_pt_hist_v5.eps}
		\label{fig:inc4096_r2_hist_v5}
	}
	\subfigure[PT frequency on INC8192]{
		\includegraphics[scale=0.43]{repet_data2/8192_sec_pt_hist.eps}
		\label{fig:inc8192_r2_hist_v5}
	}
	\subfigure[PT frequency on INC16384]{
		\includegraphics[scale=0.43]{repet_data2/16384_sec_pt_hist.eps}
		\label{fig:inc16384_r2_hist_v5}
	}
	\caption{PT Histograms of INC2048 ... INC16384~\label{fig:s9_r2_pt_hist4}}
\end{figure}

### 2017-05-24 pt_characterization/rep_check/u_s_time.tex
New draft for concrete complexity

%% done
\begin{table}[h]
\begin{center}
\begin{tabular}{|c|c|c|} \hline
%Machine & Task Length (sec) & Description & Experiment Period & Relevant \linebreak Histograms\\ \hline
%{\tt sodb9} &  INC1$\sim$INC64 & 1000 samples, each & 2017-03-02 $\sim$ 2017-03-04 & Figs.~\ref{fig:s9_r1_et_hist1},~\ref{fig:s9_r1_et_hist2},~\ref{fig:s9_r1_pt_hist1}, and~\ref{fig:s9_r1_pt_hist2}\\ \hline
%{\tt sodb9} &  INC128$\sim$INC1024 & 300 samples, each & 2017-03-04 $\sim$ 2017-03-11 & 
%Figs.~\ref{fig:s9_r1_et_hist3} and~\ref{fig:s9_r1_pt_hist3}\\ \hline
%{\tt sodb10} & INC2048 & 300 samples & 2017-03-02 $\sim$ 2017-03-09 & Figs.~\ref{fig:inc2048_r1_et_hist_v5} and~\ref{fig:inc2048_r1_hist_v5}\\ \hline
%{\tt sodb12} & INC4096 & 300 samples & 2017-02-13 $\sim$ 2017-02-27 & Figs.~\ref{fig:inc4096_r1_et_hist_v5} and~\ref{fig:inc4096_r1_hist_v5}\\ \hline
 						& w/ u time & w/ s time\\ \hline
daemon u time & 0.1 & {\bf 0.3} \\ \hline
daemon s time & -0.09 & {\bf 0.19} \\ \hline
daemon minor faults & {\bf 0.11} & {\bf 0.32} \\ \hline
%read bytes & N/A & N/A
daemon read char & 0.1 & {\bf 0.32} \\ \hline
daemon read sys calls & 0.11 & {\bf 0.32} \\ \hline
daemon write bytes & 0 & {\bf 0.26} \\ \hline
daemon write char & 0.11 & {\bf 0.32}\\ \hline
%read sys calls & N/A & N/A
\end{tabular}
\end{center}
\vspace{-.2in}
\caption{Correlation of user and system time of INC4096 with some daemon measures\label{tab:corr_table}}
\end{table}

@@

\begin{figure}[htp!]
	\centering
	\subfigure[User time vs. All daemon system time]{
		\includegraphics[scale=0.43]{u_s_time/corr_u_as_time.eps}
		\label{fig:corr_u_as_time}
	}
	\subfigure[System time vs. All daemon system time]{
		\includegraphics[scale=0.43]{u_s_time/corr_s_as_time.eps}
		\label{fig:corr_s_as_time}
	}
	\subfigure[User time vs. All daemon minor faults]{
		\includegraphics[scale=0.43]{u_s_time/corr_mnf_u_time.eps}
		\label{fig:corr_u_mnf}
	}
	\subfigure[System time vs. All daemon minor faults]{
		\includegraphics[scale=0.43]{u_s_time/corr_mnf_s_time.eps}
		\label{fig:corr_s_mnf}
	}
	\caption{Scatter plots between measures on INC4096~\label{fig:corr1}}
\end{figure}

\begin{figure}[htp!]
	\centering
	\subfigure[System time vs. All daemon read char]{
		\includegraphics[scale=0.43]{u_s_time/corr_s_rchar.eps}
		\label{fig:corr_s_rchar}
	}
	\subfigure[System time vs. All daemon read syscalls]{
		\includegraphics[scale=0.43]{u_s_time/corr_s_rsysc.eps}
		\label{fig:corr_s_rsysc}
	}
	\subfigure[System time vs. All daemon write bytes]{
		\includegraphics[scale=0.43]{u_s_time/corr_s_wbytes.eps}
		\label{fig:corr_s_wbytes}
	}
	\subfigure[System time vs. All daemon write char]{
		\includegraphics[scale=0.43]{u_s_time/corr_s_wchar.eps}
		\label{fig:corr_s_wchar}
	}
	\caption{Scatter plots between measures on INC4096~\label{fig:corr2}}
\end{figure}

>>>>

\begin{table}[h]
\begin{center}
\begin{tabular}{|c|c|c|} \hline
 						   & INC2048's u time & INC2048's s time\\ \hline
INC2048's u time  &	 -  &  0.05\\ \hline					
daemon u time & 0.56 & 0.61\\ \hline
daemon s time & 0.48 & 0.57\\ \hline
daemon minor faults &  0.53 & 0.62\\ \hline
daemon major faults & 0.55 & 0.59 \\ \hline
daemon read bytes & 0.55 & 0.59 \\ \hline
daemon read char & 0.56 & 0.61\\ \hline
daemon read sys calls & 0.57 & 0.63\\ \hline
daemon write bytes & 0.57 &  0.64\\ \hline
daemon write char & 0.53 & 0.62\\ \hline
%write sys calls & N/A & N/A\\ \hline
\end{tabular}
\end{center}
\vspace{-.2in}
\caption{Correlation of user and system time of INC2048 with some daemon measures\label{tab:corr_table2}}
\end{table}

\begin{table}[h]
\begin{center}
\begin{tabular}{|c|c|c|} \hline
 						   & INC4096's u time & INC4096's s time\\ \hline
INC4096's u time  &	 -  & -0.30 \\ \hline					
daemon u time & 0.1 & {\bf 0.3} \\ \hline
daemon s time & -0.09 & {\bf 0.19} \\ \hline
daemon minor faults & {\bf 0.11} & {\bf 0.32} \\ \hline
%read bytes & N/A & N/A
daemon read char & 0.1 & {\bf 0.32} \\ \hline
daemon read sys calls & 0.11 & {\bf 0.32} \\ \hline
daemon write bytes & 0 & {\bf 0.26} \\ \hline
daemon write char & 0.11 & {\bf 0.32}\\ \hline
%write sys calls & N/A & N/A
\end{tabular}
\end{center}
\vspace{-.2in}
\caption{Correlation of user and system time of INC4096 with some daemon measures\label{tab:corr_table}}
\end{table}

@@

\begin{figure}[htp!]
	\centering
	\subfigure[User time vs. Sum of all daemon system time]{
		\includegraphics[scale=0.43]{u_s_time/corr_u_as_time.eps}
		\label{fig:corr_u_as_time}
	}
	\subfigure[System time vs. Sum of all  daemon system time]{
		\includegraphics[scale=0.43]{u_s_time/corr_s_as_time.eps}
		\label{fig:corr_s_as_time}
	}
	\subfigure[User time vs. Sum of all  daemon minor faults]{
		\includegraphics[scale=0.43]{u_s_time/corr_mnf_u_time.eps}
		\label{fig:corr_u_mnf}
	}
	\subfigure[System time vs. Sum of all  daemon minor faults]{
		\includegraphics[scale=0.43]{u_s_time/corr_mnf_s_time.eps}
		\label{fig:corr_s_mnf}
	}
	\caption{Scatter plots between measures on INC4096~\label{fig:corr1}}
\end{figure}

\begin{figure}[htp!]
	\centering
	\subfigure[System time vs. Sum of all  daemon read char]{
		\includegraphics[scale=0.43]{u_s_time/corr_s_rchar.eps}
		\label{fig:corr_s_rchar}
	}
	\subfigure[System time vs. Sum of all  daemon read syscalls]{
		\includegraphics[scale=0.43]{u_s_time/corr_s_rsysc.eps}
		\label{fig:corr_s_rsysc}
	}
	\subfigure[System time vs. Sum of all  daemon write bytes]{
		\includegraphics[scale=0.43]{u_s_time/corr_s_wbytes.eps}
		\label{fig:corr_s_wbytes}
	}
	\subfigure[System time vs. Sum of all daemon write char]{
		\includegraphics[scale=0.43]{u_s_time/corr_s_wchar.eps}
		\label{fig:corr_s_wchar}
	}
	\caption{Scatter plots between measures on INC4096~\label{fig:corr2}}
\end{figure}

\clearpage

\subsection{Further Investigation of Some Samples}

\subsubsection{Samples in Fig.~\ref{fig:corr_u_mnf}}

\begin{table}[h]
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|} \hline
proc name (id) & u time & s time & min flt & maj flt & r bytes & r char & r sysc & w bytes & w char & w sysc\\ \hline
INC4096 (3559) & 4103920 & 36 & 0 & 0 & 0 & 1 & 1 & 0 & 0 & 0 \\ \hline
proc\_monitor (25917) & 194 & 6 & 2 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ \hline
md0\_raid1 (484) & 0 &  3 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ \hline
java (3549) & 2 & 1 & 1093 & 0 & 0 & 11480 & 20 & 0 & 0 & 0 \\ \hline
cifsd (1927) & 0 & 1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ \hline
kblockd/0 (16) & 0 & 1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ \hline
ntpd (28232) & 0 & 1 & 1 & 0 & 0 & 0 & 42 & 4096 & 7 & 0 \\ \hline
\end{tabular}
\end{center}
\caption{Observed values of measures of processes on the leftmost sample in Fig.~\ref{fig:corr_u_mnf}~\label{tab:breakdown}}
\end{table}

\begin{table}[h]
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|} \hline
proc name (id) & u time & s time & min flt & maj flt & r bytes & r char & r sysc & w bytes & w char & w sysc\\ \hline
INC4096 (3559) & 4103984 & 19 & 0 & 0 & 0 & 1 & 1 & 0 & 0 & 0 \\ \hline
proc\_monitor (25917) & 190 & 6 & 2 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ \hline
java (3549) & 2 & 1 & 1093 & 0 & 0 & 11480 & 20 & 0 & 0 & 0 \\ \hline
md0\_raid1 (484) & 0 & 3 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ \hline
ntpd (28232) & 0 & 0 & 1 & 0 & 0 & 0 & 39 & 4096 & 7 & 0 \\ \hline
java (4108) & 0 & 0  & 20 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ \hline
\end{tabular}
\end{center}
\caption{Observed values of measures of processes on the second rightmost sample in Fig.~\ref{fig:corr_u_mnf}~\label{tab:breakdown2}}
\end{table}

\begin{table}[h]
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|} \hline
proc name (id) & u time & s time & min flt & maj flt & r bytes & r char & r sysc & w bytes & w char & w sysc\\ \hline
INC4096 (3559) & 4103988 & 25 & 0 & 0 & 0 & 1 & 1 & 0 & 0 & 0 \\ \hline
proc\_monitor  (25917)  & 194 & 2 & 2 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ \hline
sshd (3609) & 8 & 4 & 1382 & 0 & 0 & 512357 & 400 & 0 & 20881 & 0 \\ \hline
bash (3611)  & 4 & 1 & 835 & 0 & 0 & 283911 & 155 & 0 & 136 & 0 \\ \hline
md0\_raid1 (484) & 0 & 3 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ \hline
java (3549) & 2 & 1 & 1093 & 0 & 0 & 11480 & 20 & 0 & 0 & 0 \\ \hline
cifsd (1927) & 0 & 2 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ \hline
java (3606) & 0 & 1 & 22 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ \hline
jbd2/md0-8 (497) & 0 & 1 & 0 & 0 & 0 & 0 & 0 & 450560 & 0 & 0 \\ \hline
kblockd/0 (16) & 0 & 1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ \hline
grep (3617) & 1 & 0 & 311 & 0 & 0 & 5417 & 11 & 0 & 0 & 0 \\ \hline
bash (3612) & 0 & 0 & 158 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ \hline
consoletype (3613) & 0 & 0 & 127 & 0 & 0 & 1956 & 6 & 0 & 7 & 0 \\ \hline
bash (3614) & 0 & 0 & 174 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ \hline
uname (3615) & 0 & 0 & 189 & 0 & 0 & 1956  & 6 & 0 & 7 & 0 \\ \hline
sshd (3610) & 0 & 0 & 425 & 0 & 0 & 22656 & 29 & 0 & 4630 & 0 \\ \hline
sshd (2105) & 0 & 0 & 14 & 0 & 0 & 0 & 0 & 0 & 594 & 0 \\ \hline
bash (3618) & 0 & 0 & 170 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ \hline
id (3619) & 0 & 0 & 225 & 0 & 0 & 4352 & 12 & 0 & 2 & 0 \\ \hline
ntpd (28232) & 0 & 0 & 1 & 0 & 0 & 0 & 42 & 4096 & 7 & 0 \\ \hline
bash (3616) & 0 & 0 & 131 & 0 & 0 & 0 & 0 & 0 & 61 & 0 \\ \hline
\end{tabular}
\end{center}
\caption{Observed values of measures of processes on the rightmost sample in Fig.~\ref{fig:corr_u_mnf}~\label{tab:breakdown1}}
\end{table}

\subsubsection{Samples in Fig.~\ref{fig:corr_s_wbytes}}

\begin{table}[h]
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|} \hline
proc name (id) & u time & s time & min flt & maj flt & r bytes & r char & r sysc & w bytes & w char & w sysc\\ \hline
INC4096 (3559) & 4103981 & 14 & 0 & 0 & 0 & 1 & 1 & 0 & 0 & 0 \\ \hline
proc\_monitor (25917) & 194 & 2 & 2 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ \hline
md0\_raid1 (484) & 0 & 5 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ \hline
java (3549) & 2 & 1 & 1093 & 0 & 0 & 11480 & 20 & 0 & 0 & 0 \\ \hline
flush-9:0 (3548) & 0 & 2 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ \hline
ntpd (28232) & 0 & 0 & 1 & 0 & 0 & 0 & 42 & 4096 & 7 & 0 \\ \hline
java (4585) & 0 & 0 & 20 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ \hline
\end{tabular}
\end{center}
\caption{Observed values of measures of processes on the leftmost sample in Fig.~\ref{fig:corr_s_wbytes}~\label{tab:breakdown4}}
\end{table}

\begin{table}[h]
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|} \hline
proc name (id) & u time & s time & min flt & maj flt & r bytes & r char & r sysc & w bytes & w char & w sysc\\ \hline
INC4096 (3559) & 4103958 & 44 & 0 & 0 & 0 & 1 & 1 & 0 & 0 & 0 \\ \hline
proc\_monitor (25917) & 194 & 2 & 2 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ \hline
sshd (4877) & 10 & 4 & 1382 & 0 & 0 & 519568 & 392 & 0 & 20868 & 0 \\ \hline
sshd (4886) & 10 & 3 & 1383 & 0 & 0 & 515456 & 393 & 0 & 20868 & 0 \\ \hline
grep (4888) & 6 & 1 & 994 & 0 & 0 & 287034 & 154 & 0 & 136 & 0 \\ \hline
grep (4879) & 3 & 2 & 991 & 0 & 0 & 286801 & 159 & 0 & 136 & 0 \\ \hline
java (3549) & 2 & 1 & 1093 & 0 & 0 & 11480 & 20 & 0 & 0 & 0 \\ \hline
md0\_raid1 (484) & 0 & 3 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ \hline
sshd (4878) & 2 & 1 & 424 & 0 & 0 & 22403 & 26 & 0 & 4268 & 0 \\ \hline
jbd2/md0-8 (497) & 0 & 2 & 0 & 0 & 0 & 0 & 0 & 696320 & 0 & 0 \\ \hline
flush-9:0 (3548) & 0 & 2 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ \hline
cifsd (1927) & 0 & 1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ \hline
kblockd/0 (16) & 0 & 1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ \hline
grep (4892) & 0 & 1 & 309 & 0 & 0 & 5417 & 11 & 0 & 0 & 0 \\ \hline
grep (4883) & 1 & 0 & 310 & 0 & 0 & 5417 & 11 & 0 & 0 & 0 \\ \hline
id (4894) & 0 & 0 & 226 & 0 & 0 & 4352 & 12 & 0 & 2 & 0 \\ \hline
bash (4884) & 0 & 0 & 164 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ \hline
id (4885) & 0 & 0 & 226 & 0 & 0 & 0 & 12 & 0 & 2 & 0 \\ \hline
sshd (2105) & 0 & 0 & 28 & 0 & 0 & 0 & 0 & 0 & 1188 & 0 \\ \hline
sshd (4887) & 0 & 0 & 425 & 0 & 0 & 22403 &26 & 0 & 4268 & 0 \\ \hline
ntpd (20232) & 0 & 0 & 1 & 0 & 0 & 0 & 42 & 4096 & 7 & 0 \\ \hline
bash (4880) & 0 & 0 & 165 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ \hline
uname (4890)  & 0 & 0 & 190 & 0 & 0 & 1956  & 6 & 0 & 7 & 0 \\ \hline
bash (4891) & 0 & 0 & 128 & 0 & 0 & 0 & 0 & 0 & 61 & 0 \\ \hline
java  (4874) & 0 & 0 & 20 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ \hline
bash (4893) & 0 & 0 & 164 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ \hline
uname (4881)  & 0 & 0 & 191 & 0 & 0 & 1956  & 6 & 0 & 7 & 0 \\ \hline
bash (4889) & 0 & 0 & 165 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ \hline
\end{tabular}
\end{center}
\caption{Observed values of measures of processes on the second rightmost sample in Fig.~\ref{fig:corr_s_wbytes}~\label{tab:breakdown5}}
\end{table}

\begin{table}[h]
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|} \hline
proc name (id) & u time & s time & min flt & maj flt & r bytes & r char & r sysc & w bytes & w char & w sysc\\ \hline
INC4096 (3559) & 4103948 & 45 & 0 & 0 & 0 & 1 & 1 & 0 & 0 & 0 \\ \hline
proc\_monitor (25917) & 190 & 10 & 2 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ \hline
md0\_raid1 (484) & 0 & 5 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ \hline
jbd2/md0-8 (497) & 0 & 3 & 0 & 0 & 0 & 0 & 0 & 471040 & 0 & 0 \\ \hline
java (3549) & 2 & 1 & 1093 & 0 & 0 & 11480 & 20 & 0 & 0 & 0 \\ \hline
cifsd (1927) & 0 & 2 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ \hline
flush-9:0 (3548) & 0 & 1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ \hline
java (5022) & 1 & 0 & 21 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ \hline
ntpd (28232) & 0 & 0 & 1 & 0 & 0 & 0 & 42 & 4096 & 7 & 0 \\ \hline
\end{tabular}
\end{center}
\caption{Observed values of measures of processes on the rightmost sample in Fig.~\ref{fig:corr_s_wbytes}~\label{tab:breakdown6}}
\end{table}
